# Documentation

```{r setup2, include=FALSE}
library(tidyverse)
```

## Evaluate a Laboratory Notebook {#lab-notebook}

***Description:*** *The laboratory or research notebook is a fundamental documentation method for many researchers. But for how ubiquitous the lab notebook is, documentation can sometimes be lacking. The ideal laboratory notebook allows someone with similar training as you to be able to follow everything you did in your research. This exercise prompts you to review an old entry within your laboratory notebook to evaluate if your documentation is sufficient for reproducing your work.*

***Instructions:*** *You will need a laboratory notebook entry from 6-12 months ago to do this exercise. Once you have the entry, read through it to try to understand what you did on that day. Answer the exercise questions to evaluate the entry and identify any note keeping improvements to make.*

---

**Date of lab notebook entry being evaluated:** \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

**Read the entry and summarize the work you did on that date:**

&nbsp;

&nbsp;

&nbsp;

**How easy was it to understand what you did from your notes? Could you reproduce your work solely from the information in your notes?**

&nbsp;

&nbsp;

&nbsp;

**What worked well with your note keeping?**

&nbsp;

&nbsp;

&nbsp;

**What would you improve about your note keeping?**

&nbsp;

&nbsp;

&nbsp;

**List one change you plan to make to take better research notes:**

&nbsp;

&nbsp;

&nbsp;

## Write a Project-Level README.txt {#readme-txt}

***Description:*** *Data files living on a computer often need extra documentation for someone to understand what research they correspond to. In particular, it is useful to record the most basic project information and store it in the top-level folder of each research project. This can be done with a README.txt. The name, "README", indicates that the file conveys important information and the file type, TXT, can be opened by many different software programs, making the content maximally accessible. This exercise walks you through the key information needed in a project-level README.txt file. The same information can also be recorded at the front of a physical laboratory notebook.*

***Instructions:*** *Pick a research project and answer the following questions. Copy all of the text into a TXT file and save it with the name “README.txt”. Store this file in the top-level of the project folder on your computer, alongside the project files.*

***Source:*** *This exercise was adapted from the "Project Close Out Checklist" [@briney_project_2020].*

---

**What is the title of the project?**

&nbsp;

&nbsp;

&nbsp;

**What is the project description?**

&nbsp;

&nbsp;

&nbsp;

**What is the time period the project was done over?**

&nbsp;

&nbsp;

&nbsp;

**Who worked on the project?**

&nbsp;

&nbsp;

&nbsp;

**Where are the files are stored?**

&nbsp;

&nbsp;

&nbsp;

**How are files organized? Are any naming conventions used and, if so, what are they (see [Chapter 3](#file-organization-and-naming))?**

&nbsp;

&nbsp;

&nbsp;

## Create a Data Dictionary {#data-dictionary}

***Description:*** *Ideally, a spreadsheet is formatted with a row of variable names at the top, followed by rows of data going down. This makes easy for data to be used in any data analysis software (interoperability is a good thing) but makes it impossible to document a spreadsheet within the file itself. For this reason, it’s useful to create a data dictionary to describe the spreadsheet so that others can interpret the data. This exercise walks you through the major information you should record for each variable in the spreadsheet, adding up to a complete dictionary to accompany the spreadsheet file.*

***Instructions:*** *Fill out the question in each row for each variable in the spreadsheet; note that you will likely have more variables than columns in this table. Copy this information into a text document and save it next to the spreadsheet. It is useful to save the data dictionary with the same root name as its data file by appending "\_dictionary” on the end of the file name; for example, the data dictionary for the file “myData.xlsx” would be “myData\_dictionary.txt”.*

***Source:*** *This exercise was adapted from the "Leveling Up Data Management" [@briney_leveling_2023].*

---

``` {r dictionary-table, echo = FALSE}
dictionary <- tibble(Question = 
                       c("Variable name",
                         "Variable description",
                         "Variable units",
                         "Relationship to other variables",
                         "Variable coding values and meanings",
                         "Known issues with the data",
                         "Anything else to know about the data?"),
                     Variable1 = c("", "", "", "", "", "", ""),
                     Variable2 = c("", "", "", "", "", "", ""),
                     Variable3 = c("", "", "", "", "", "", ""))
knitr::kable(dictionary)
```
