# Data Storage

```{r setup4, include=FALSE}
library(tidyverse)
```

All research data needs to be stored and backed up, but it can be frustrating to pick these systems and ensure that they are working correctly. This chapter consists of two exercises: a worksheet to document available storage and backup options and decide between them; and a procedure for testing that a backup system is working.

## Store and Back Up the Data {#storage}

***Description:*** *Research data needs to be stored and backed up reliably so that important data is not lost. But storage is commonly a challenge, as institutions don’t always offer uniform options for storage and backup. This exercise prompts you to examine the storage and backup systems available to you, either free or paid, as well as options outside of your institution, before determining which is the best set of options for your data.*

***Instructions:*** *Fill out the first three tables for storage and backup systems that are: 1) institutional and free; 2) institutional and paid; and 3) outside of your institution. Examine all of the options, evaluating them based on the criteria listed below the first three tables to pick your ideal storage and backup configuration. **Note that this exercise works best for data under 1 TB in size that has no security restrictions.***

---

**What storage or backup systems are already available to you, such as through your institution or workplace, at no cost?**

``` {r storage-no-cost, echo = FALSE}
dictionary <- tibble(Question = 
                       c("System name",
                         "Is it storage or backup?",
                         "What is the hardware type?",
                         "Is the system backed up?",
                         "For backup systems, is backup automatic?",
                         "Is the system local or remote?",
                         "How is there a limit to storage capacity?",
                         "Who manages the system?",
                         "Is it easy or difficult to use?"),
                     "System 1" = c("", "", "", "", "", "", "", "", ""),
                     "System 2" = c("", "", "", "", "", "", "", "", ""),
                     "System 3" = c("", "", "", "", "", "", "", "", ""))
knitr::kable(dictionary)
```

**What storage or backup systems are available to you, such as through your institution or workplace, at a cost?**

``` {r storage-cost, echo = FALSE}
dictionary <- tibble(Question = 
                       c("System name",
                         "Is it storage or backup?",
                         "What is the cost?",
                         "What is the hardware type?",
                         "Is the system backed up?",
                         "For backup systems, is backup automatic?",
                         "Is the system local or remote?",
                         "How is there a limit to storage capacity?",
                         "Who manages the system?",
                         "Is it easy or difficult to use?"),
                     "System 1" = c("", "", "", "", "", "", "", "", "", ""),
                     "System 2" = c("", "", "", "", "", "", "", "", "", ""),
                     "System 3" = c("", "", "", "", "", "", "", "", "", ""))
knitr::kable(dictionary)
```

**Are there other storage or backup systems that you can use? **

``` {r storage-other, echo = FALSE}
dictionary <- tibble(Question = 
                       c("System name",
                         "Is it storage or backup?",
                         "What is the cost?",
                         "What is the hardware type?",
                         "Is the system backed up?",
                         "For backup systems, is backup automatic?",
                         "Is the system local or remote?",
                         "How is there a limit to storage capacity?",
                         "Who manages the system?",
                         "Is it easy or difficult to use?"),
                     "System 1" = c("", "", "", "", "", "", "", "", "", ""),
                     "System 2" = c("", "", "", "", "", "", "", "", "", ""),
                     "System 3" = c("", "", "", "", "", "", "", "", "", ""))
knitr::kable(dictionary)
```

**Optimize your storage and backups on the following considerations:**

1. You need one storage system that will hold all of your data files, is easy to use, and is managed by someone you trust.
2. You need at least one backup – preferably two – that will hold all of your data files, is managed by someone you trust, is easy to use, and backs up automatically.
3. At least one backup should be in a different location than your main storage system for disaster resiliency.
4. Balance cost with making sure that storage/backup systems are managed by trustworthy parties and are not difficult to use.

**Pick your storage and backup systems:**

``` {r storage-backup, echo = FALSE}
dictionary <- tibble(Storage = c("&nbsp;"),
                     "Backup 1" = c("&nbsp;"),
                     "Backup 2" = c("&nbsp;"))
knitr::kable(dictionary)
```



## Test Your Backup {#backup}

***Description:*** *Backups are super important for your data, so it’s always good to test that your backups are still working. Nothing is worse than losing your data from your primary storage and then realizing that your backup isn’t working either. Beyond checking that your backup is working, it’s also good to know how to recover your files so that you don’t have to learn this for the first time while panicking about lost data. This short exercise walks you through getting a file off your backup to test that it is working and to learn how the data-recovery process works.*

***Instructions:*** *Pick a backup system and a file to recover and work through the steps. The hard part of this exercise is finding instructions for file recovery and recovering the file, which vary by backup system.*

---

1. Identify where your data is backed up.
2. Find instructions for recovering data from your backup system.
3. Pick a data file from your computer.
4. Follow the instructions from step 2 to get a copy of the data file from step 3 out of your backup system.
5. If this process didn’t work, fix your backup system. If this process did work, congrats your backup is working and you know how to recover your files!
